\section*{Schedules}
\label{sec:schedules}

\scheduleSection{Basic concepts}{4}{Space and time, frames of reference, Galilean transformations. Newton's laws. Dimensional analysis. Examples of forces, including gravity, friction and Lorentz.}

\scheduleSection{Newtonian dynamics of a single particle}{8}{Equation of motion in Cartesian and plane polar coordinates. Work, conservative forces and potential energy, motion and the shape of the potential energy function; stable equilibria and small oscillations; effect of damping.

\noindent
Angular velocity, angular momentum, torque.

\noindent
Orbits: the \(u\para{\theta}\) equation; escape velocity; Kepler's laws; stability of orbits; motion in a repulsive potential (Rutherford scattering).

\noindent
Rotating frames: centrifugal and Coriolis forces. *Brief discussion of Foucault pendulum.*}

\scheduleSection{Newtonian dynamics of systems of particles}{2}{Momentum, angular momentum, energy. Motion relative to the centre of mass; the two body problem. Variable mass problems; the rocket equation.}

\scheduleSection{Rigid bodies}{3}{Moments of inertia, angular momentum and energy of a rigid body. Parallel axis theorem. Simple examples of motion involving both rotation and translation (e.g. rolling).}

\scheduleSection{Special relativity}{7}{The principle of relativity. Relativity and simultaneity. The invariant interval. Lorentz transformations in
\(\para{1 + 1}\)-dimensional spacetime. Time dilation and length contraction. The Minkowski metric for \(\para{1 + 1}\)-dimensional spacetime.

\noindent
Lorentz transformations in \(\para{3 + 1}\) dimensions. 4-vectors and Lorentz invariants. Proper time. 4-velocity and 4-momentum. Conservation of 4-momentum in particle decay. Collisions. The Newtonian limit.}